---
title: "Homework 3"
author: "Kelly Craig"
date: "May 27, 2019"
output:
  pdf_document: default
  html_document: default
---
#Load Packages

```{r echo=FALSE, include =FALSE, results = 'hide'}
library(tidyverse)
library(Lahman)
```

#Number 1
Turn data into tibble then print

```{r Number 1, echo=TRUE}
Pitching <- tbl_df(Pitching)
Pitching
```

#Number 2
Name the new tibble PitchingID. Select for columns that end in ID and W,L, ERA columns. Print PitchingID tibble.   

```{r Number 2, echo=TRUE}
PitchingID <- Pitching %>% select(ends_with("ID"), W, L, ERA)
PitchingID
```

#Number 3
Filter years 2010 to 2015 in the yearID column Using the previous dataset PitchingID.  

```{r Number 3, echo=TRUE}
PitchingIDYear <- PitchingID %>% filter(yearID>= 2010 & yearID <= 2015)
PitchingIDYear
```

#Number 4
Add a column to the data (PitchingIDYear) for win loss percentage. 
 
```{r Number 4, echo=TRUE}
PitchingIDYearWL <- PitchingIDYear %>% mutate(WLpercentage = ( W / (W + L)))
PitchingIDYearWL
```

#Number 5
Sort PitchingIDYearWL data set by the Win/Loss Percentage column in descending order and name the new data set PitchingIDYearWLSorted.

```{r Number 5, echo=TRUE}
PitchingIDYearWLSorted <- arrange(PitchingIDYearWL, desc(WLpercentage))
PitchingIDYearWLSorted
```

#Number 6
Group the PitchingIDYearWLSorted dataset by team ID and year. Filter year ID with rows from years 2010 to 2015. Find the average of ERA and remove NA values. 
```{r Number 6, echo=TRUE}
PitchingAvgERA <- PitchingIDYearWLSorted %>% group_by(teamID,yearID) %>% filter(yearID %in% (c(2010,2011,2012,2013,2014,2015))) %>% summarise(PitchingAvgERA=mean(ERA, na.rm=TRUE))
PitchingAvgERA
```

#Number 7
Turn the PitchingAvgERA dataset from long format into wide using the spread function. Column names are year and the value to spread out is average ERA 

```{r Number 7, echo=TRUE}
Wide <- PitchingAvgERA %>% spread(key = yearID , value = PitchingAvgERA)
knitr::kable(Wide)
```

#Number 8

```{r Number 8, echo=TRUE}
Wide <- Wide %>% replace_na(list("2010" = 7.198065, "2011" = 4.736818))
Wide <- Wide[-c(11),]

knitr::kable(Wide)
```

