---
title: "Homework 5"
author: "Kelly Craig"
date: "May 30, 2019"
output:
  pdf_document: default
  html_document: default
---

```{r echo=FALSE, include =FALSE, results = 'hide'}
library(tidyverse)
library(dplyr)
library(haven)
library(readxl)
```
#Number 1
A delimiter is a sequence of one or more characters used to specify the boundary between separate regions in data. The most common delimiter is the comma character.  

#Number 2
Both `library()` `and require()` are used to attach and load add-on packages which are already installed. `require()` is used inside functions and will output a warning and continue if the package is not found. `library()` will output an error. 

#Number 3
`read_csv()` and `read.csv()` both read in comma separated value files. The Base R function is `read.csv()` and the tidyverse fuction is `read_csv()`. `read.csv()` reads the character variables as factors and it is slower compared to `read_csv()`.  

#Number 4a
Read in the BreastCancer dat file and name it cancerData.
```{r, echo=TRUE}
cancerData <- read_tsv("C:/Users/Kelly/Documents/BreastCancer.dat")
cancerData <- tbl_df(cancerData)
cancerData
```

#Number 4b
Select for only the size column in the cancerData data. 
```{r, echo=TRUE}
cancerDataSize <- cancerData %>% select("size")
cancerDataSize
```

#Number 4c
Print just the top 3 rows from the cancerData data. 
```{r, echo=TRUE}
cancerDataRow <- cancerData[1:3, ]
cancerDataRow
```

#Number 4d
select for just the size and meno columns in the cancerData data. Group by meno, then summarize, the mean, standard deviation, and IQR for the size values.
```{r, echo=TRUE}
cancerData <- cancerData %>% select("size", "meno")
cancerData %>% group_by(meno) %>% summarise(mean(size), sd(size), IQR(size))
```

#Number 5a
Read in the text file mosquito
```{r, echo=TRUE}
mosquitoData <- read_delim("C:/Users/Kelly/Documents/mosquito.txt", delim = "&")
 tbl_df(mosquitoData)
```

#Number 5b
Find the column names of mosquitoData. Read in mosquitoData2 using read_tsv and name them the same column names of mosquitoData. 

```{r, echo=TRUE}
names(mosquitoData)
mosquitoData2 <- read_tsv("C:/Users/Kelly/Documents/mosquito2.txt", col_names = c("Day","Cage","trt","Response"))
tbl_df(mosquitoData2)

```

# 5c
Combine mosquitoData and mosquitoData2 using rbind.
```{r, echo=TRUE}
mosquitoFullData <- rbind(mosquitoData, mosquitoData2)
tbl_df(mosquitoFullData)
```

#5d
The rbind function can take a sequence of a vector, matrix or data-frame arguments and combine by columns or rows. It does not only work on dataframes.  

#5e
Create a column called LifeTime in hours and a column called Duration which is a category of Short, Long, or Medium. Append both columns onto the existing mosquito dataset.
```{r, echo=TRUE}
mm <- mosquitoFullData %>% mutate(LifeTime = (Response*24))
mm$Duration <- ifelse(mm$Day < 20, 'Short', ifelse(mm$Day > 40, 'Long', 'Medium'))
mosquitoFullData <- mm
mm
```

#5f
Write the mosquito data file to a csv file.

```{r, echo=TRUE}
write_csv(mosquitoFullData, "C:/Users/Kelly/Documents/mosquitoFullData.csv")
```

#6a
Use the haven package to read in the Stata data.
```{r, echo=TRUE}
Effort <- read_stata("C:/Users/Kelly/Documents/effort.dta")
Effort
```

#6b
Create a subset showing effort values above 10.
```{r, echo=TRUE}
Effort <- subset(Effort, effort > 10)
Effort
```

#7
Read in the second tab on the excel file Chickens and rename it to sheepData.
```{r, echo=TRUE}
sheepData <- read_excel("C:/Users/Kelly/Documents/Chickens.xlsx", sheet = "Sheep")
sheepData
```


